---
title: "Cheatsheet-tidyr"
author: "Jiahui Tang"
date: "2017/10/7"
output: html_document
---
# CheatSheet-`tidyr`

*This is a cheatsheet to remind me of some tidyr functions, and it will help me with the later homeworks in STAT545 class.*

## 4 Main Functions

| tidyr Function    | Special Powers
|-------------------|----------------------------
|  `gather`         | long format\*
|  `spread`         | wide format\*
|  `unite`          | Unite multiple columns into one.
|  `separate`       | Separate one column into multiple columns.

```{r}
#use mtcars in datasets to show deoms
library(tidyr)
library(dplyr)
<<<<<<< HEAD
=======
opts_chunk$set(comment=NA, tidy=FALSE, message = FALSE, warnings = FALSE)
>>>>>>> 53d41757b083c74c811c5657fa3625b82530afd8
mtcars$car <- rownames(mtcars)
mtcars <- mtcars[, c(12, 1:11)]
head(mtcars)
```

## Demos

```R
gather(data, key, value, …, na.rm = FALSE, convert = FALSE)
spread(data, key, value, fill = NA, convert = FALSE, drop = TRUE)
unite(data, col, …, sep = “_”, remove = TRUE
separate(data, col, into, sep = “[^[:alnum:]]+”, remove = TRUE, 
convert = FALSE, extra = “warn”, fill = “warn”, …)
```
### ***gather()***

```{r}
#the columns except car are gathered into two columns, named attribute and value respectively
mtcarsNew <- mtcars %>% gather(attribute, value, -car)
head(mtcarsNew)
tail(mtcarsNew)
```

```{r}
#Gather all columns between map and gear, while keeping the carb and car columns unchanged
mtcarsNew <- mtcars %>% gather(attribute, value, mpg:gear)
head(mtcarsNew)
#Continuous
mtcarsNew <- mtcars %>% gather(mpg:drat, key = "attribute", value ="value", -car)
unique(mtcarsNew$attribute)
head(mtcarsNew)
#Discontinuous
mtcarsNew <- mtcars %>% gather(`gear`,`carb`,key = "attribute", value = "value", -car)
head(mtcarsNew)
unique(mtcarsNew$attribute)
```

### ***spread()***

```{r}
#Separate one column into multiple columns.
mtcarsSpread <- mtcarsNew %>% spread(attribute, value)
head(mtcarsSpread)
```

### ***unite()***

```{r}
#First make a data frame
set.seed(1)
date <- as.Date('2017-10-07') + 0:14
hour <- sample(1:24, 15)
min <- sample(1:60, 15)
second <- sample(1:60, 15)
event <- sample(letters, 15)
data <- data.frame(date, hour, min, second, event)
data
```

```{r}
dataNew <- data %>%unite(datehour, date, hour, sep = ' ') %>%unite(datetime, datehour, min, second, sep = ':')
dataNew
```

### ***separate()***

```{r}
data1 <- dataNew %>%separate(datetime, c('date', 'time'), sep = ' ') %>%separate(time, c('hour', 'min', 'second'), sep = ':')
data1
```

## Links

[gather From tidyr v0.7.1 by Hadley Wickham](https://www.rdocumentation.org/packages/tidyr/versions/0.7.1/topics/gather)
<<<<<<< HEAD

[spread From tidyr v0.7.1 by Hadley Wickham](https://www.rdocumentation.org/packages/tidyr/versions/0.7.1/topics/spread)

[unite From tidyr v0.7.1 by Hadley Wickham](https://www.rdocumentation.org/packages/tidyr/versions/0.7.1/topics/unite)

=======
[spread From tidyr v0.7.1 by Hadley Wickham](https://www.rdocumentation.org/packages/tidyr/versions/0.7.1/topics/spread)
[unite From tidyr v0.7.1 by Hadley Wickham](https://www.rdocumentation.org/packages/tidyr/versions/0.7.1/topics/unite)
>>>>>>> 53d41757b083c74c811c5657fa3625b82530afd8
[separate From tidyr v0.7.1 by Hadley Wickham](https://www.rdocumentation.org/packages/tidyr/versions/0.7.1/topics/separate)
[R-tidyr](http://www.cnblogs.com/nxld/p/6060533.html)

