---
title: "hw04-Tang-Jiahui"
author: "Jiahui Tang"
date: "2017/10/5"
output: github_document
---

```{r}
library(tidyverse)
library(tidyr)
library(gapminder)
library(knitr)
library(countrycode) # To get the countrycode
library(easyGgplot2) # To put multiple graphs on the same page using ggplot2
#library(geonames)
library(dplyr)
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gapminder))
knitr::opts_chunk$set(fig.width=13, fig.height=10)
```

## General data reshaping and relationship to aggregation

***Activity #1***

  + Make you own [cheatsheet for tidyr](https://github.com/Tangjiahui26/STAT545-hw-Tang-Jiahui/blob/master/hw04/Cheatsheet-tidyr.md).
    - I gave demos for 4 main tidyr functions on the cheatsheet, and used `mtcars` dataset that is a typical wide format data_frame.
  
***Activity #2***

  + Make a tibble with one row per year and columns for life expectancy for two or more countries.
    - Use knitr::kable() to make this table look pretty in your rendered homework.
    - Take advantage of this new data shape to scatterplot life expectancy for one country against that of another.

*I am here to select five Asian countries: China, Japan, India, Thailand, Singapore.*
```{r}
A1 <- gapminder %>% 
  filter(country %in% c("China", "Japan", "India", "Thailand", "Singapore")) %>% 
  select(country, year, lifeExp) %>% 
  spread(key = country, value = lifeExp)

knitr::kable(A1, caption = "Life Expectancy by Countries")
```

*I used `ggplot2` to make plots for one country(China) against that of another. And use ggplot2.multiplot to put the four graphs on the same page.*

```{r}
Plot1 <- A1 %>% 
  ggplot(aes(x = China, y = Japan)) +
  geom_point(size = 4, alpha = 0.8, aes(color = factor(year))) +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  theme_bw() +
  theme(axis.title.x = element_text(size=15),
        axis.title.y = element_text(size=15),
        plot.title = element_text(hjust = 0.5))+
  labs(title="Life Expectancy of China vs Japan")+
  scale_colour_discrete("year") +
  scale_x_continuous(breaks = c(40, 50, 60, 70, 80)) +
  scale_y_continuous(breaks = c(40, 50, 60, 70, 80))

Plot2 <- A1 %>% 
  ggplot(aes(x = China, y = India)) +
  geom_point(size = 4, alpha = 0.8, aes(color = factor(year))) +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  theme_bw() +
  theme(axis.title.x = element_text(size=15),
        axis.title.y = element_text(size=15),
        plot.title = element_text(hjust = 0.5))+
  labs(title="Life Expectancy of China vs Inida")+
  scale_colour_discrete("year") +
  scale_x_continuous(breaks = c(40, 50, 60, 70, 80)) +
  scale_y_continuous(breaks = c(40, 50, 60, 70, 80))

Plot3 <- A1 %>% 
  ggplot(aes(x = China, y = Thailand)) +
  geom_point(size = 4, alpha = 0.8, aes(color = factor(year))) +
  geom_smooth(method = "lm", se = FALSE, color = "yellow") +
  theme_bw() +
  theme(axis.title.x = element_text(size=15),
        axis.title.y = element_text(size=15),
        plot.title = element_text(hjust = 0.5))+
  labs(title="Life Expectancy of China vs Thailand")+
  scale_colour_discrete("year") +
  scale_x_continuous(breaks = c(40, 50, 60, 70, 80)) +
  scale_y_continuous(breaks = c(40, 50, 60, 70, 80))

Plot4 <- A1 %>% 
  ggplot(aes(x = China, y = Singapore)) +
  geom_point(size = 4, alpha = 0.8, aes(color = factor(year))) +
  geom_smooth(method = "lm", se = FALSE, color = "green") +
  theme_bw() +
  theme(axis.title.x = element_text(size=15),
        axis.title.y = element_text(size=15),
        plot.title = element_text(hjust = 0.5))+
  labs(title="Life Expectancy of China vs Singapore")+
  scale_colour_discrete("year") +
  scale_x_continuous(breaks = c(40, 50, 60, 70, 80)) +
  scale_y_continuous(breaks = c(40, 50, 60, 70, 80))

# Multiple graphs on the same page
ggplot2.multiplot(Plot1,Plot2,Plot3,Plot4, cols=2)
```

*We can easily compare the life expectancy of China against that of another from the plots above.*

## Join, merge, look up

***Activity #1***

  + Create a second data frame, complementary to Gapminder. Join this with (part of) Gapminder using a dplyr join function and make some observations about the process and result. Explore the different types of joins. 

*I used countrycode() to get the countrycode of Asian countries, selected some variables for a new data_frame called `first_gapminder`. Obviously, the new data_frame has 5 columns represent continent, country, lifeExp, year and countryCode respectively.*

```{r}
gapminder_code <- gapminder %>%
  mutate(countryCode = countrycode(country, "country.name", "iso2c"))
  knitr::kable(head(gapminder_code))
  
first_gapminder <- gapminder_code %>% 
  select(continent, country, lifeExp, year, countryCode) %>% 
  filter(continent == "Asia" & year == 2007)

knitr::kable(first_gapminder)
```

*We should create a second_gapminder data_frame to realize join functions, so I picked 8 countries with their continent, language and national flower, etc. *

```{r}
country <- c("China", "Japan", "India", "Thailand", "Singapore", "Canada", "Germany", "Netherlands")
continent <- c("Asia","Asia","Asia","Asia","Asia","Americas", "Europe","Europe")
Languages <- c("Mandarin","Japanese","Hindi/English","Dai","English", "English", "German", "Dutch")
NATO <- c(0, 0, 0, 0, 0, 1, 1, 1)
National_flower <- c("Peony", "Cherry Blossom", "Nelumbo nucifera", "Cassia fistula", "Vanda 'Miss Joaquim'", "Sugar Maple", "Blue Bottle", "Tulipa")

second_gapminder <- data.frame(country, continent, Languages, NATO, National_flower)
knitr::kable(second_gapminder)
```

### *left_join*

*We can find that left_join1 will return all rows from second_gapminder and all rowa from second_gapminder and first_gapminder. Left_join2 is the opposite of left_join1.*

```{r}
left_join1 <- left_join(second_gapminder, first_gapminder, by=c("country", "continent"))
knitr::kable(left_join1)
```

```{r}
left_join2 <- left_join(first_gapminder, second_gapminder)
knitr::kable(left_join2)
```

### *inner_join*

*We can find that inner_join returns all rows from second_gapminder where there are matching values in first_gapminder, and all columns from both.*

```{r}
inner_join1 <- inner_join(second_gapminder, first_gapminder)
knitr::kable(inner_join1)
```

### *semi_join*

*We can find that it will return all rows from second_gapminder where there are matching values in first_gapminder, keeping just columns from second_gapminder. Semi_join2 is the opposite of semi_join1.*

```{r}
semi_join1 <- semi_join(second_gapminder, first_gapminder)
knitr::kable(semi_join1)
```

```{r}
semi_join2 <- semi_join(first_gapminder, second_gapminder)
knitr::kable(semi_join2)
```

### *anti_join*

*Return all rows from second_gapminder where there are not matching values in first_gapminder, keeping just columns from second_gapminder. *

```{r}
anti_join1 <- anti_join(second_gapminder, first_gapminder)
knitr::kable(anti_join1)
```

*Return all rows from first_gapminder where there are not matching values in second_gapminder, keeping just columns from first_gapminder. *

```{r}
anti_join2 <- anti_join(first_gapminder, second_gapminder)
knitr::kable(anti_join2)
```

*full_join*

+ Return all rows and all columns from both x and y. Where there are not matching values, returns NA for the one missing. This is a mutating join.

```{r}
full_join1 <- full_join(second_gapminder, first_gapminder)
knitr::kable(full_join1)
```
  
  