---
title: "hw02-Tang-Jiahui"
author: "Jiahui Tang"
date: "2017/9/22"
output:
  html_document:
    keep_md: yes
  pdf_document: default
---
## Load Packages

```{r}
library(gapminder)
library(tidyverse)
```

## Smell test the data

- Q1: Is it a data.frame, a matrix, a vector, a list?
- Q2: What’s its class?
```{r}
#typeof(gapminder)
#mode(gapminder)
class(gapminder)
str(gapminder)
```
  A1: It is a data.frame.
 
  A2: Gapminder is actually a tibble(data.frame tbl/tbl_df), which is useful for `dplyr`. 

Acutally I am kind of confused with `typeof()`, `mode()` and `class()`. There is a clear explanation on [stackoverflow](https://stackoverflow.com/questions/8855589/a-comprehensive-survey-of-the-types-of-things-in-r-mode-and-class-and-type). I believe  `mode()` would  get  the type or storage mode of an object ,while `typeof()` function would be more specific. The `class()` is used to define/identify what "type" an object is from the point of view of object-oriented programming in R.

- Q3: How many variables/columns?
- Q4: How many rows/observations?
- Q5: Can you get these facts about “extent” or “size” in more than one way? Can you imagine different functions being useful in different contexts?
- Q6: What data type is each variable?
```{r}
ncol(gapminder)
length(gapminder)
nrow(gapminder)
dim(gapminder)
summary(gapminder)
str(gapminder)
head(gapminder)
```
  A3: 6. As we can see above, we can use `ncol()`, `length()` and `dim()` to find out the number of variables/columns.
 
  A4: 1704. Similarly, `nrow()`, `dim()` can be used to look up the number of rows/observations.
 
  A5: As we know above, we can absolutely use different functions. I think some function like `nrow()` and `ncol()` are more specific to get direct answers, while others like `dim()`, `summary()` and `str()` would give basic informations and we can figure out what we want from the results.
 
  A6: From the results of `str()` and `head()`, we can get the type of each variable:country and continent -> Factor,year and pop -> Integer, LifeExp and gdpPercap -> num(double).
 
## Explore individual variables

We can easily find categorical variables and quantitative variables from the results above:

*categorical variables*: country, continent
*quantitative variables*:year, lifeExp, pop, gdpPercap

We will pick `country` and `gdpPercap` to explore.
- Q1: What are possible values (or range, whichever is appropriate) of each variable?
  A1: For categorical variables, we can use some functions as follows:
```{r}
print(gapminder$country)
summary(gapminder$country)
gapminder %>% 
  distinct(country)
```
  A1: We can use `print()` to print all values of `country` beacuse it is actually a Factor of gapminder. What's more, `summary()` and `distinct()` can also give the levels of `country`.

  A1: For quantitative variables, we can use some functions as follows:
```{r}
print(gapminder$gdpPercap)
summary(gapminder$gdpPercap)
gapminder %>% 
  summarise(min_gdpPercap=min(gdpPercap),max_gdpPercap=max(gdpPercap),mean_gdpPercap=mean(gdpPercap))
```
  A1:Similarly, We can use `print()` to print all values of `gdpPercap`. What's more, `summary()` and `summarise()` can also give the range of `gdpPercap`.
  
- Q2: What values are typical? What’s the spread? What’s the distribution? Etc., tailored to the variable at hand.

In this part, categorical variable `continent` and quantitative variable `gdpPercap` will be used to explore.
```{r}
#typical value
summary(gapminder$continent)
table(gapminder$gdpPercap)
```
  A2: From above we can find that the typical value of `continent` is Africa, since it appears 624 times. For the quantitative variable `gdpPercap`, it seems does not have typical value because all values appear 1 times.
  
```{r}
#spread
#way1:plot the data
plot(gapminder$continent)
hist(gapminder$gdpPercap)
#way2:calculating summary statistics like sd
gapminder %>% 
  summarise(sd = sd(gdpPercap))
```
  A2: We can tell this by plotting the data (boxplots or histograms) by using `plot()` and `hist()`, or calculating summary statistics like the standard deviation of that variable.
  
```{r}
#distribution
plot(gapminder$continent)
hist(gapminder$gdpPercap)
```
  
  A3: For the distribution, we can also plot the data and figure out the trend of values by using `plot()` and `hist()` functions.
  
## Explore various plot types

1. A scatterplot of two quantitative variables. 
  + scatterplot1: This is the scatterplot of `year` and `log10(pop)`. We can add aesthetic mapping of transparency.Then, we can make other plots facetted by `continent` and fit a smoother through the data for each continent.
```{r}
#scatterplot1
p <- ggplot(gapminder, aes(x = year, y = log10(pop)))
p <- p + geom_point(alpha = 0.5)
p
p1 <- p + facet_wrap(~ continent, scales = "free_y")
p1
p2 <- p1 + geom_smooth(lwd = 1, se = FALSE) + aes(color = continent)
p2
```
 
  + scatterplot2: A plot of `log10(gdpPercap)` and `lifeExp`, facetted by continent and fit a regression line through the data for each continent.
```{r}
#scatterplot2
p3 <- ggplot(gapminder, aes(x = log(gdpPercap), y = lifeExp))
p3 <- p3 + geom_point(aes(color = continent), alpha = 0.5)
p3 <- p3 + facet_wrap(~ continent, scales = "free_y")
p3 <- p3 + geom_smooth(lwd = 1, se = FALSE, method = 'lm') 
p3
```
 
  + scatterplot3: A plot of `log10(gdpPercap)` and `lifeExp`, facetted by countries from Americas and fit a smoother through the data for each country.
```{r}
#scatterplot3
Americas <- filter(gapminder, continent == "Americas")
p4 <- ggplot(Americas, aes(x = log(gdpPercap), y = lifeExp))
p4 <- p4 + geom_point(alpha = 0.5)
p4 <- p4 + facet_wrap(~ country, scales = "free_y")
p4 <- p4 + geom_smooth(lwd = 1, se = FALSE) 
p4
```

2. A plot of one quantitative variable. Maybe a histogram or densityplot or frequency polygon.
  + Make a densityplot of `log10(pop)` by using `density()` and `plot()`.
```{r}
den_pop <- density(log10(gapminder$pop))
plot(den_pop, main = "Densityplot of log10(pop)") 
polygon(den_pop, col = "red", border = "green")
```
 
  + Make a histogram of `log10(pop)` by using `hist()`.
```{r}
hist(log10(gapminder$pop), col="red", main="Histogram of log10(pop)")
```

3. A plot of one quantitative variable and one categorical. Maybe boxplots for several continents or countries.
  + Make a boxplot for `log10(pop)` and `continent`.
```{r}
boxplot(log10(pop) ~ continent,data = gapminder, 
        main = "Boxplots for log10(pop) and continent", 
        xlab = "Continent", ylab = "log10(pop)", col="red")
```

## Use filter(), select() and %>%

Take all entries of Canada occuring from 1950-2010, and select the `year`, and `gdpPercap` columns, then piping into `ggplot()`.
```{r}
out1 <- gapminder %>% 
   filter(country == "Canada",
           year <= 2010, year >= 1950) %>% 
    select(year, gdpPercap) %>% 
  ggplot(aes(x = gdpPercap, y = year)) + geom_point(aes(color = year))
out1
```

## But I want to do more!

I thought it would be wrong if running the code showing below because we are more likely to use `"%in%"` instead of `"=="`. We cannot get all the data for Rwanda and Afghanistan if we use `"=="`.
```{r}
filter(gapminder, country == c("Rwanda", "Afghanistan"))
filter(gapminder, country %in% c("Rwanda", "Afghanistan"))
```
