---
title: "hw02-Tang-Jiahui"
author: "Jiahui Tang"
date: "2017/9/22"
output:
  html_document:
    keep_md: yes
  pdf_document: default
---
## Load Packages

```{r}
library(gapminder)
library(tidyverse)
```

## Smell test the data

- Q1: Is it a data.frame, a matrix, a vector, a list?
- Q2: What’s its class?
```{r}
#typeof(gapminder)
#mode(gapminder)
class(gapminder)
str(gapminder)
```
 A1: It is a data.frame.
 
 A2: Gapminder is actually a tibble(data.frame tbl/tbl_df), which is useful for `dplyr`. 

Acutally I am kind of confused with `typeof()`, `mode()` and `class()`. There is a clear explanation on [stackoverflow](https://stackoverflow.com/questions/8855589/a-comprehensive-survey-of-the-types-of-things-in-r-mode-and-class-and-type). I believe  `mode()` would  get  the type or storage mode of an object ,while `typeof()` function would be more specific. The `class()` is used to define/identify what "type" an object is from the point of view of object-oriented programming in R.

- Q3: How many variables/columns?
- Q4: How many rows/observations?
- Q5: Can you get these facts about “extent” or “size” in more than one way? Can you imagine different functions being useful in different contexts?
- Q6: What data type is each variable?
```{r}
ncol(gapminder)
length(gapminder)
nrow(gapminder)
dim(gapminder)
summary(gapminder)
str(gapminder)
head(gapminder)
```
 A3: As we can see above, we can use `ncol()`, `length()` and `dim()` to find out the number of variables/columns.
 
 A4: Similarly, `nrow()`, `dim()` can be used to look up the number of rows/observations.
 
 A5: As we know above, we can absolutely use different functions. I think some function like `nrow()` and `ncol()` are more specific to get direct answers, while others like `dim()`, `summary()` and `str()` would give basic informations and we can figure out what we want from the results.
 
 A6: From the results of `str()` and `head()`, we can get the type of each variable:country and continent are Factor,year and pop are Integer, LifeExp and gdpPercap are num(double).
