---
title: "Hw01-Tang-Jiahui"
author: "Jiahui Tang"
date: "2017/9/18"
output:
  html_document:
    keep_md: yes
  pdf_document: default
---
## Load Packages

```{r}
library(gapminder)
library(tidyverse)
```

## Displays the structure of gapminder by using str()
```{r}
str(gapminder)
```

## Print head and tail of gapminder
```{r}
head(gapminder)
tail(gapminder)
```

## Print basic info of gapminder
```{r}
names(gapminder)
dim(gapminder)
length(gapminder)
nrow(gapminder)
summary(gapminder)
```

## Make figures:
```{r}
plot(lifeExp ~ year, gapminder)
plot(lifeExp ~ log(gdpPercap), gapminder)
```

## Explore the lifeExp variable from gapminder
```{r}
head(gapminder$lifeExp)
summary(gapminder$lifeExp)
hist(gapminder$lifeExp)
```

## How factors can be put to work in figures
The `continent` factor is easily mapped into “facets” or colors and a legend by the `ggplot2` package. *Making figures with `ggplot2` is covered elsewhere so feel free to just sit back and enjoy these plots or blindly copy/paste.*
```{r}
p <- ggplot(filter(gapminder, continent != "Oceania"),
            aes(x = gdpPercap, y = lifeExp)) # just initializes
p <- p + scale_x_log10() # log the x axis the right way
p + geom_point() # scatterplot
p + geom_point(aes(color = continent)) # map continent to color
p + geom_point(alpha = (1/3), size = 3) + geom_smooth(lwd = 3, se = FALSE)
p + geom_point(alpha = (1/3), size = 3) + facet_wrap(~ continent) + geom_smooth(lwd = 1.5, se = FALSE)