---
title: "hw03-Tang-Jiahui"
author: "Jiahui Tang"
date: "2017/9/30"
output:
  html_document:
    keep_md: yes
  pdf_document: default
---

## But I want do more!

+ Layout stretch goal: get table and figure side-by-side. [This gist](https://gist.github.com/jennybc/e9e9aba6ba18c72cec26) might get you started.
*Applying this layout stretch to task03.*

***The follow codes are kind of messy because I added CSS codes. You can find the result on hw03-Tang-Jiahui-I_want_do_more.html, or see the screenshot in /STAT545-hw-Tang-Jiahui/pics folder. ***

```{r}
library(ggplot2)
suppressMessages(library(dplyr))
library("gapminder")
gtbl <- tbl_df(gapminder)
```
<style type="text/css">
.twoC {width: 100%}
.clearer {clear: both}
.twoC .table {max-width: 50%; float: left}
.twoC img {max-width: 50%; float: right}
</style>

<div class="twoC">

```{r results = 'asis', echo=FALSE}
tbl1 <- gapminder %>% 
  group_by(year) %>% 
  summarise(mean_LifeExp = mean(lifeExp), 
            weighted_by_pop = weighted.mean(lifeExp, pop),
            weighted_by_gdpPercap = weighted.mean(lifeExp, gdpPercap))
knitr::kable(tbl1)
```

```{r echo=FALSE}
T3 <- gapminder %>% 
  group_by(year) %>% 
  summarise(mean_LifeExp = mean(lifeExp), 
            weighted_by_pop = weighted.mean(lifeExp, pop),
            weighted_by_gdpPercap = weighted.mean(lifeExp, gdpPercap))

P12 <- ggplot(T3, aes(x = year, y = LifeExp)) +
  geom_line(aes(y = mean_LifeExp, color = "mean_LifeExp")) +
  geom_line(aes(y = weighted_by_pop, color = "weighted_by_pop")) +
  geom_line(aes(y = weighted_by_gdpPercap, color = "weighted_by_gdpPercap")) +
  labs(title = "Means of Life Expectancy for different years")
P12
```
</div>
<div class="clearer"></div>