---
title: "hw06-Tang-Jiahui"
author: "Jiahui Tang"
date: "2017/11/3"
output:  
pdf_document: 
    latex_engine: xelatex
---
```{r}
knitr::opts_chunk$set(warning = F)
library(tidyverse)
library(stringr)
```

## Character data

Read and work the exercises in the [Strings chapter](http://r4ds.had.co.nz/strings.html) or R for Data Science.

### Exercises14.2.5

+ In code that doesn’t use stringr, you’ll often see`paste()` and`paste0()`. What’s the difference between the two functions? What stringr function are they equivalent to? How do the functions differ in their handling of NA?

*Answer: I believe`paste0(..., collapse)`is equivalent to`paste(..., sep = "", collapse)`. We can use`str_c()`in stringr to replace them. However,`str_replace_na()` will be used when handling with NA if we use`str_c`, while`paste()` and`paste0()`won't need that. From the results below, we can find that`str_c()`returns NA if any arugment is NA while`paste()`and`paste0()`will replace NA with "NA".*

```{r}
#Usage:
#paste (..., sep = " ", collapse = NULL)
#paste0(..., collapse = NULL)
x <- c(1:3,"ab","cd","ef", NA)
paste(x, sep = " ",collapse = NULL)
str_c(str_replace_na(x), sep = " ")
paste0(x, collapse = ",")
str_c(str_replace_na(x), collapse = ",")
str_c("a",NA)
paste("a",NA)
paste0("a",NA)
```

+ In your own words, describe the difference between the sep and collapse arguments to`str_c()`.

*Answer: `sep`is used to insert string between arguments of str_c, while`collapse`is the string used to combine input vectors into single string. See examples below.*

```{r}
x <- c("aa","bb","cc")
str_c("Letter", x, sep = ", ")
str_c(x, collapse = ", ")
```

+ Use str_length() and str_sub() to extract the middle character from a string. What will you do if the string has an even number of characters?

*Answer: I would choose the str_length(x)/2 if the string has an even number of chars.*

```{r}
x <- c("1","12","123","1234","12345","123456")
middle <- function(x) {
  if(str_length(x)%%2 == 0){
   res <- str_length(x)/2
  } else{
   res <- (str_length(x) + 1)/2
  }
  return(res)
}
mid <- middle(x)
str_sub(x, mid, mid)
```

+ What does str_wrap() do? When might you want to use it?

*Answer: Wrap strings into nicely formatted paragraphs. I think it is useful to handle long text like the example below.*

```{r}
x <- c("What does str_wrap() do?
       When might you want to use it?")
cat(str_wrap(x,width = 10, exdent = 2), "\n")
```

+ What does str_trim() do? What’s the opposite of str_trim()?

*Anwser: `str_trim()`is to delete whitespace from start and end of string.`str_pad`to add whitespace.*

```{r}
str_trim(" What does str_trim() do? ")
x <- "What does str_trim() do?"
str_pad(x, str_length(x)+2, side = "both")
```

+ Write a function that turns (e.g.) a vector c("a", "b", "c") into the string a, b, and c. Think carefully about what it should do if given a vector of length 0, 1, or 2.

```{r}
vector_to_string <- function(x) {
  if(length(x) > 1){
    str_c(str_c(x[-length(x)], collapse = ", "), x[length(x)], sep = ", and ")
  } else{
    return(x)
  }
}
x <- c("a", "b", "c","d") 
vector_to_string(x)
```

### Exercises14.3.1.1

+ Explain why each of these strings don’t match a \: "\", "\\", "\\\".

*Answer: From the results below, we can find that "\" would escape the next character, "\\" would become \ in regexps, "\\\" works like the combination of "\" and "\\" as it would become a backblash then escape the next character.*

```{r}
backslash <- "a\b"
backslash1 <- "a\\b"
backslash2 <- "a\\\b"
writeLines(backslash)
writeLines(backslash1)
writeLines(backslash2)
str_view(c("abc", "a\\b", "bef"), "\\\\")
```

+ How would you match the sequence "'\ ?

*Anwser: We should string "\"\\'\\\\" to match  "'\ as below.*

```{r}
str_view(c("abc", 'a"\'\\b', "bef"), "\"\\'\\\\")
```


+ What patterns will the regular expression \..\..\.. match? How would you represent it as a string?

*Answer: The regular express \..\..\.. matches any strings that have a dot followed by any characters,then another dot with character，then another dot with character.*

```{r}
str_view(c("abc", ".a.b.c", "bef"), "\\..\\..\\..")
```

### Exercises14.3.2.1

+ How would you match the literal string "$^$"?

*Answer：We can use '^\\$\\^\\$$' to match. *

```{r}
str_view(c("abc", "$^$", "a$^$a"), "^\\$\\^\\$$")
```

+ Given the corpus of common words in stringr::words, create regular expressions that find all words that:
   1. Start with “y”.
   2. End with “x”
   3. Are exactly three letters long. (Don’t cheat by using str_length()!)
   4. Have seven letters or more.
   
Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.

*Anwser: We can use regular expressions show below to find all words.*

```{r}
str_view(stringr::words, "^y", match = TRUE)
str_view(stringr::words, "x$", match = TRUE)
str_view(tail(stringr::words), "^...$", match = TRUE)
str_view(head(stringr::words), "^.......", match = TRUE)
```

### Exercises14.3.3.1
+ Create regular expressions to find all words that:

  1. Start with a vowel.

  2. That only contain consonants. (Hint: thinking about matching “not”-vowels.)

  3. End with ed, but not with eed.

  4. End with ing or ise.

```{r}
str_view(head(stringr::words), "^[aeiou]", match = TRUE)
str_view(stringr::words, "[aeiou]", match = FALSE)
str_view(stringr::words, "[^e]ed$", match = TRUE)
str_view(stringr::words, "ing$|ise$", match = TRUE)
```

+ Empirically verify the rule “i before e except after c”.

```{r}
str_view(stringr::words, "cei|[^c]ie", match = TRUE)
str_view(stringr::words, "cie|[^c]ei", match = TRUE)
```

+ Is “q” always followed by a “u”?

*Answer: From the result we may find it is true that "q" always followed by a "u".*

```{r}
str_view(stringr::words, "q[^u]", match = TRUE)
```

+ Write a regular expression that matches a word if it’s probably written in British English, not American English.

*Answer: Taking "-ize/-ise" and "-se/-ze" as examples, we may use regular expression to match British English words.*

```{r}
str_view(c("summarize","summarise","defense","defence"), "ce$|ize$", match = TRUE)
```

+ Create a regular expression that will match telephone numbers as commonly written in your country.

```{r}
str_view(c("778-111-1111","028-8888-8888"), "\\d\\d\\d-\\d\\d\\d-\\d\\d\\d\\d", match = TRUE)
```

### Exercises14.3.4.1

+ Describe the equivalents of ?, +, * in {m,n} form.

*Answer: ? is equal to {,1}, + is equal to {1,} and \* is equal to {0,}*

+ Describe in words what these regular expressions match: (read carefully to see if I’m using a regular expression or a string that defines a regular expression.)

1. ^.*$
2. "\\{.+\\}"
3. \d{4}-\d{2}-\d{2}
4. "\\\\{4}"

*Anwser: The first regular expression matches all words. The second one matches all words(at least one character) surrounded by curly braces. The third one matches XXXX-XX-XX(X represents digits). The last one matches four backslashes.*

```{r}
str_view(stringr::words, "^.*$", match = FALSE)
str_view(c("{a}","a{aaaa}","aa"), "\\{.+\\}", match = TRUE)
str_view(c("1234-56-78","a{a}","aa"), "\\d{4}-\\d{2}-\\d{2}", match = TRUE)
str_view(c("\\\\\\\\","a{a}","aa"), "\\\\{4}", match = TRUE)
```

+ Create regular expressions to find all words that:

1. Start with three consonants.
2. Have three or more vowels in a row.
3. Have two or more vowel-consonant pairs in a row.

```{r}
str_view(stringr::words, "^[^aeoiu]{3,}", match = TRUE)
str_view(stringr::words, "[aeoiu]{3,}", match = TRUE)
str_view(head(stringr::words), "([aeoui][^aeoiu]){2,}", match = TRUE)
```

+ Solve the beginner regexp crosswords at https://regexcrossword.com/challenges/beginner.

*Anwser: help bobe oooo **// 1984*

### Exercises14.3.5.1

+ Describe, in words, what these expressions will match:

1. (.)\1\1
2. "(.)(.)\\2\\1"
3. (..)\1
4. "(.).\\1.\\1"
5. "(.)(.)(.).*\\3\\2\\1"

*Answer: The first one means the same characters showing three times. The second one represents a pair of characters and its reversal. The third one matches two charcaters followed by the same two characters. The forth matches a character followed by any character, then character same as the first, then any other character and the same character again. The last one matches three characters followed by 0 or more characters, the the three characters in reverse. *

```{r}
str_view(c("aa","aaa"), "(.)\\1\\1", match = TRUE)
str_view(c("abba","abab"), "(.)(.)\\2\\1", match = TRUE)
str_view(c("abcd","aaaa","a0a0"), "(..)\\1", match = TRUE)
str_view(c("a1a2a","a.a.a","abcde"), "(.).\\1.\\1", match = TRUE)
str_view(c("abc123cba","abcderf"), "(.)(.)(.).*\\3\\2\\1", match = TRUE)

```


+ Construct regular expressions to match words that:

1. Start and end with the same character.

2. Contain a repeated pair of letters (e.g. “church” contains “ch” repeated twice.)

3. Contain one letter repeated in at least three places (e.g. “eleven” contains three “e”s.)

```{r}
str_view(c("abc123cba","abcderf"), "^(.).*\\1$", match = TRUE)
str_view(c("abcab","abcderf","cdabcab"), ".*(..).*\\1", match = TRUE)
str_view(c("12311","abcaa","abcde"), ".*(.).*\\1.*\\1", match = TRUE)
```

### Exercises14.4.2

+ For each of the following challenges, try solving it by using both a single regular expression, and a combination of multiple str_detect() calls.

1. Find all words that start or end with x.

2. Find all words that start with a vowel and end with a consonant.

3. Are there any words that contain at least one of each different vowel?

```{r}
#1.1 A sigle regexp
words[str_detect(words,"^x|x$")]
#1.2 Combination of mutiple str_detect() calls
start_x <- str_detect(words,"^x")
end_x <- str_detect(words,"x$")
words[start_x|end_x]

#2.1 A sigle regexp
head(str_subset(words, "^[aeiou].*[^aeiou]$"))
#2.2 Combination of mutiple str_detect() calls
start_vowel <- str_detect(words,"^[aeiou]")
end_consonant <- str_detect(words,"[^aeiou]$")
head(words[start_vowel&end_consonant])

#3.1 A sigle regexp
str_subset(words, "[^a]&[^e]&[^i]&[^o]&[^u]")
#3.2 Str_detect()
words[str_detect(words,"a")&str_detect(words,"b")&str_detect(words,"c")&str_detect(words,"d")&str_detect(words,"e")]
```

+ What word has the highest number of vowels? What word has the highest proportion of vowels? (Hint: what is the denominator?)

*Anwser: From the result we can see "appropriate" "associate"   "available"   "colleague"   "encourage"   "experience"  "individual"  "television" have the highest number of vowels. For the second question, we can use str_length(words) as the denominator.*

```{r}
#highest number of vowels
max(str_count(words, "[aeiou]"))
words[which(str_count(words, "[aeiou]") == 5)]

#highest proportion of vowels
highest_vowels <- str_count(words, "[aeiou]")/str_length(words)
words[which(highest_vowels == max(highest_vowels))]
```

### Exercises14.4.3.1

+ In the previous example, you might have noticed that the regular expression matched “flickered”, which is not a colour. Modify the regex to fix the problem.

*Anwser: We can add \b to solve this proble, like`str_c("\\b(", str_c(colours, collapse = "|"), ")\\b")`.*

+ From the Harvard sentences data, extract:

1. The first word from each sentence.
2. All words ending in ing.
3. All plurals.

*Anwser: For question3, we just consider the situation that words with more than 3 characters ending with "s". From the result, we may find that there are some false postives like "makes".*

```{r}
# First word
head(str_extract(sentences,"[a-zA-Z]+"))

# All words ending in ing
ing <- str_extract_all(sentences[str_detect(sentences, "\\b[a-zA-Z]+ing\\b")],"\\b[a-zA-Z]+ing\\b",simplify = TRUE)
head(ing)

# All plurals
plurals <- str_extract_all(sentences[str_detect(sentences, "\\b[a-zA-Z]{3,}s\\b")],"\\b[a-zA-Z]{3,}s\\b",simplify = TRUE)
head(plurals)
```

### Exercises14.4.4.1

+ Find all words that come after a “number” like “one”, “two”, “three” etc. Pull out both the number and the word.

```{r}
number <-"(one|two|three|four|five|six|seven|eight|nine|ten) ([^ ]+)"
after_number <- sentences %>% 
  str_subset(number) %>% 
  head(10)
after_number %>% 
  str_extract(number)
```

+ Find all contractions. Separate out the pieces before and after the apostrophe.

```{r}
contraction <- "([A-Za-z]+)'([A-Za-z]+)"
con <- sentences %>% 
  str_subset(contraction) %>% 
  head(10)
con %>% 
    str_match(contraction)
```

### Exercises14.4.5.1

+ Replace all forward slashes in a string with backslashes.

```{r}
x <- c("/apple", "pe/ar", "bana/na")
str_replace(x, "[////]", "\\\\")
writeLines(x)
```

+ Implement a simple version of str_to_lower() using replace_all().

```{r}
x <- c("housE", "carS", "PeoplE")
str_replace_all(x, c("E" = "e", "S" = "s", "P" = "p"))
```


+ Switch the first and last letters in words. Which of those strings are still words?

```{r}
switch <- str_replace(words,"(^[a-zA-Z])([a-zA-Z]*)([a-zA-Z]$)", "\\3\\2\\1")
head(switch)
words[words==switch]
```

### Exercises14.4.6.1

+ Split up a string like "apples, pears, and bananas" into individual components.

```{r}
x <- c("apples, pears, and bananas")
str_split(x, boundary("word"))[[1]]
```

+ Why is it better to split up by boundary("word") than " "?

*Answer: It is better to split up by boundary("word") because there are also punctuation and not just whitespace.*

+ What does splitting with an empty string ("") do? Experiment, and then read the documentation.

*Answer: string"" will split a string into single characters including punctuations and whitespaces*

```{r}
str_split("ab.cd. e ", "")[[1]]
```

### Exercises14.5.1

+ How would you find all strings containing \ with regex() vs. with fixed()?

```{r}
str_subset(c("a\\b", "ab"), "\\\\")
str_subset(c("a\\b", "ab"), fixed("\\"))
```

+ What are the five most common words in sentences?

```{r}
str_extract_all(sentences, boundary("word")) %>%
  unlist() %>%
  str_to_lower() %>%
  tibble() %>%
  set_names("words") %>%
  group_by(words) %>%
  count(sort = TRUE) %>%
  head(5)
```

### Exercises14.7.1

+ Find the stringi functions that:

1. Count the number of words.
2. Find duplicated strings.
3. Generate random text.

*Answer: We can use`stri_count_words` to count the number of words.`stri_duplicated` and`stri_duplicated_any` can be used to find duplicated strings. We can use stri_rand_strings to generate Random Strings.*

```{r}
stringi::stri_count_words("words and sentences")
stringi::stri_duplicated(c("a", "b", "a", NA, "a", NA), fromLast=TRUE)
stringi::stri_duplicated_any(c("a", "b", "a", NA, "a", NA))
stringi::stri_rand_strings(2, 5)
```

+ How do you control the language that stri_sort() uses for sorting?

*Answer: We can use`opts_collator` arugment in`stri_sort(str, decreasing = FALSE, na_last = NA, ...,opts_collator = NULL)`.*
  
```{r}
stringi::stri_sort(c("hladny", "chladny"), locale="pl_PL")
```
