---
title: "Work with the singer data"
author: "Jiahui Tang"
date: "2017/11/7"
output: github_document
---

```{r, message=FALSE}
knitr::opts_chunk$set(warning = F)
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(singer))
suppressPackageStartupMessages(library(stringr))
suppressPackageStartupMessages(library(forcats))
suppressPackageStartupMessages(library(purrr))
suppressPackageStartupMessages(library(repurrrsive))
suppressPackageStartupMessages(library(ggmap))
suppressPackageStartupMessages(library(leaflet))
suppressPackageStartupMessages(library(mapview))
suppressPackageStartupMessages(library(htmlwidgets))
suppressPackageStartupMessages(library(webshot))
knitr::opts_chunk$set(fig.width=10, fig.height=5)
```

## Work with the`singer`data

+ The singer_location dataframe in the singer package contains geographical information stored in two different formats: 1. as a (dirty!) variable named city; 2. as a latitude / longitude pair (stored in latitude, longitude respectively). The function revgeocode from the ggmap library allows you to retrieve some information for a pair (vector) of longitude, latitude (warning: notice the order in which you need to pass lat and long). Read its manual page.

+ Use purrr to map latitude and longitude into human readable information on the band’s origin places. Notice that revgeocode(... , output = "more") outputs a dataframe, while revgeocode(... , output = "address") returns a string: you have the option of dealing with nested dataframes.
   You will need to pay attention to two things:
   
    - Not all of the track have a latitude and longitude: what can we do with the missing information? (filtering, …)
    - Not all of the time we make a research through revgeocode() we get a result. What can we do to avoid those errors to bite us? (look at possibly() in purrr…)

*As for the track without a latitude and longitude, we need to filter all rows with latitude and longitude are NAs. Then we apply map2() to call revgeocode() for all pairs of longitude and latitude.*

*When revgeocode() goes wrong, there will be a error like this:*
```R
reverse geocode failed - bad location? location = "-87.63241"reverse geocode failed - bad location? location = "41.88415"
```
*we can use`possibly(revgeocode, NA)`to avoid this.*
    
```{r, message=FALSE}
#View(singer_locations)
#First we need to filter all rows with latitude and longitude are NAs.
filter_NA_locations <- singer_locations %>% 
  filter(!is.na(latitude) | !is.na(longitude)) %>% 
      mutate(id = 1:nrow(.)) %>% 
      filter(id <= 20)
#glimpse(filter_NA_locations)

#Then we use map2 to apply revgeocode
loc <- map2(filter_NA_locations$longitude,
                                filter_NA_locations$latitude, 
                                ~ revgeocode(c(.x, .y)))
locations <- cbind(location = loc,city = filter_NA_locations$city)
knitr::kable(locations)
```

+ Then we should figure out wether the place in city corresponds to the information you retrieved.

```{r}
city_new<-filter_NA_locations %>% 
 select(city) %>% 
 separate(city,into = c("1","2","3"),sep=" ") 
city_new <- mapply(str_replace_all,city_new,"[[:punct:]]","") 

knitr::kable(city_new)

loc_chr <- as.character(loc)
loc_chr_new <- str_extract_all(loc_chr[str_detect(loc_chr,
                                              "\\, [A-Z0-9].*[a-z]\\,|\\b[A-Z]{2,}\\b")],
                           "\\, [A-Z0-9].*[a-z]\\,|\\b[A-Z]{2,}\\b",simplify = TRUE)
City <- str_replace_all(loc_chr_new[,1],", |,", "")
loc_chr_new[,1] = City
knitr::kable(loc_chr_new)

a <- (loc_chr_new[,1]==city_new[,1])
b <- (loc_chr_new[,1]==city_new[,2])
c <- (loc_chr_new[,1]==city_new[,3])
d <- (loc_chr_new[,2]==city_new[,1])
e <- (loc_chr_new[,2]==city_new[,2])
f <- (loc_chr_new[,2]==city_new[,3])
g <- (loc_chr_new[,3]==city_new[,1])
h <- (loc_chr_new[,3]==city_new[,2])
i <- (loc_chr_new[,3]==city_new[,3])
result <- (a | b | c | d | e |f |g |h |i)
result
```


*Finally We can use leaflet() to p*

```{r}
map <- leaflet()  %>%   
addTiles() %>%
addCircles( lat=filter_NA_locations$latitude,lng=filter_NA_locations$longitude,
            popup = filter_NA_locations$title)

saveWidget(map, "map.html", selfcontained = FALSE)
webshot("map.html", file = "map.png",
        cliprect = "viewport")

mapshot(map, file = "./map.png")
```

